%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{soul}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Tariq Soliman} \\ \vspace{1pt}
  \small +614 23 696 614$|$ \href{mailto:x@x.com}{\ul{t.soliman@uq.net.au}}
  $|$
  \href{https://linkedin.com/in/tariq-soliman}{\ul{linkedin.com/in/tariq-soliman/}} $|$
  \href{https://linktr.ee/tariqsoliman}{\ul{linktr.ee/tariqsoliman}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Queensland (UQ)}{St Lucia, QLD}
{Bachelor of Engineering (Hons) and Master of Engineering, Major in Mechatronics}{Feb. 2019 -- Nov. 2024}
\resumeSubSubheading{First Class Honours - 6.8/7 GPA}{}
\resumeSubheading
{National University of Singapore (NUS)}{Singapore}
{Exchange Program}{Aug. 2022 -- Feb. 2023} \resumeSubheading
{Westpac}{Singapore}
{W100 Asian Exchange Scholar \& Leadership Development Program}{Sep. 2022} \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\resumeSubheading
{Graduate Digital Engineer}{Jan. 2024 -- Present}
{Hatch}{Brisbane, QLD}
\resumeItemListStart
\resumeItem{Supported a digital twin of Dugald River Mine (DRM) zinc flotation processing
  plant (fixing bugs/adding features). The digital twin utilises a combination of
  deep learning to simulate the operations and Particle Swarm Optimisation to
  optimise the control variables}
\resumeItem{Investigated error detection and correction techniques for the DRM Flotation
  Twin and added explainability metrics for model training (e.g Sobol Sensitivity
  Analysis, SHAP Values)}
\resumeItem{Researched applications of drones with computer vision for asset monitoring and
  predictive maintenance}
\resumeItem{Implemented a combination of deep learning and traditional computer vision
  techniques for locating concrete pillars and segmenting surface voids}
\resumeItem{Utilised research in Visual Simultaneous Localisation and Mapping in ROS2 with
  RGB and RGBD cameras for mapping GPS denied environments}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Dec. 2024 - Present}
{The University of Queensland}{St Lucia, QLD}
\resumeItemListStart
\resumeItem{Investigated dimension importance estimation with deep learning embeddings
  generated for information retrieval}
\resumeItem{\sloppy Building on work from \href{https://doi.org/10.48550/arXiv.2205.13147}{\ul{Matryoshka Respresentation Learning}} and \href{https://doi.org/10.1145/3626772.3657691}{\ul{Dimension Importance Estimation for Dense Information Retrieval}}
  to try and improve retrieval performance by choosing a subset of dimensions for
  each query}
\resumeItemListEnd

\resumeSubheading
{Tutor}{Mar. 2019 -- Nov. 2024}
{The University of Queensland, ITAR, Cluey Learning \& Privately}{St Lucia, QLD}
\resumeItemListStart
\resumeItem{UQ Courses: Programming for Engineers, Introduction to Computer Systems, Robotics and Automation}
\resumeItem{Lead tutor for courses at UQ. Responsibilities included running tutorials and
  presenting technical content, training new tutors, helping students with assignments,
  helping course coordinators draft assessments, helping to write tests for code, marking assessments}
\resumeItem{Also for the Indigenous Tutorial Assistance and Retention (ITAR)
  program, online for Cluey Learning, privately for high school students}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Dec. 2022 -- Feb. 2023}
{Singapore Sports Institute}{Singapore}
\resumeItemListStart
\resumeItem{Implemented a custom deep learning model in keras that could classify a subset
  of fencing movements based on data from four Inertial Measurement Units}
\resumeItem{Collected data from seven athletes for training the model and achieved 75-80\%
  accuracy on windows of data from an eighth unseen athlete}
\resumeItem{Developed an application with a GUI in PyQt (Qt for Python)}
\resumeItemListEnd

\resumeSubheading
{First Year Engineering Student Mentor}{Feb. 2022 -- Apr. 2022}
{The University of Queensland}{St Lucia, QLD}
\resumeItemListStart
\resumeItem{Welcomed new engineering students to UQ and helped to answer questions about
  starting university}
\resumeItem{Encouraged engagement in university life and culture}
\resumeSubHeadingListEnd

\resumeSubheading{Research Assistant}{Nov. 2021 -- Feb. 2022}
{The University of Queensland}{St Lucia, QLD}
\resumeItemListStart
\resumeItem{Helped to develop the GUI for a MacOS app for sonification of astronomical
  surveys (like Google Maps for space with sound)}
\resumeItem{Used SwiftUI and helped modify a Javascript library that used JQuery for the
  surveys}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Pose Detection with Pretrained ViTs} $|$ \emph{Python, PyTorch}}{Feb. 2023 -- June 2023}
\resumeItemListStart
\resumeItem{Performed transfer learning on ViTs pretrained using DINO, MAE and MSN methods inspired by the paper \href{https://doi.org/10.48550/arXiv.2204.12484}{\ul{\textit{ViTPose: Simple Vision Transformer Baselines for Human Pose Estimation}}}}
\resumeItem{Training with the COCO Keypoints dataset led to 0.847 $AP_{.5}$ and
  0.569 $AP_{.5:.95}$}
\resumeItem{Presented a live inference demonstration using the top-down approach with YOLO
  for detecting people}
\resumeItem{Visualised attention maps}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Admin App for Tutoring Business} $|$ \emph{React, Expo (React Native), Typescript, Firebase}}{Jan. 2021 -- March 2024}
\resumeItemListStart
\resumeItem{Developing a mobile app that allows tutors to report their hours}
\resumeItem{Developing a web app interface for admin}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Robotics Projects} $|$ \emph{Python, ROS2, C, C++, Keras, Embedded Programming}}{Feb. 2019 -- Present}
\resumeItemListStart
\resumeItem{Designed and manufactured a robot that could autonomously collect coffee beans
  buried in sand. I was responsible for localisation using a camera and ArUco
  markers and control algorithms}
\resumeItem{Designed and manufactured a robot that can find the centre of a test area and
  shoot infra-red targets with a laser pointer}
\resumeItem{Implemented an IoT robot that could turn to face people by recognising their
  shoes}
\resumeItem{Used ROS2 to program a robot to perform Simulataneous Localisation And Mapping
  (SLAM) with autonomous path planning in order to map and explore an unseen test
  area}
\resumeItem{Helped manufacture and program a robot to collect coffee beans autonomously
  from a sand pit with localisation using ArUco markers}
\resumeItemListEnd
{\textbf{Misc. Projects} $|$ \emph{Verilog, Vivado, Assembly (ARM), Solidity, React, Javascript}}{Aug. 2022 -- Dec. 2022}
\resumeItemListStart
\resumeItem{Implemented parts of an ARM processor at RTL level with verification on an FPGA}
\resumeItem{Created a multisignature wallet on the blockchain with Solidity with a web app
  interface}
\resumeItem{Created a \href{https://tariqs.com.au/}{\ul{personal blog}} to share things I am learning about.}
\resumeItem{Completed \href{https://adventofcode.com/}{\ul{Advent of Code}} 2023 and 2024 \href{https://github.com/TSoli/advent-of-code}{\ul{with all 50 stars in C++}}}
\resumeItem{Set up a homelab/server using spare PC parts. Runs Virtual Machines in Proxmox
  including Ubuntu Server and TrueNAS with access via Wireguard VPN. Other
  services are run in docker containers on the Ubuntu Server VM}
\resumeItemListEnd
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: Python, C, C++ (modern), JavaScript, TypeScript, Java, Bash, Promela, Matlab, Swift, Lua, Verilog, Assembly (AVR \& ARM), Solidity} \\
                \textbf{Frameworks}{: React, Expo (React Native), Node.js, PyTorch, Tensorflow (with keras), ROS2, PyQt, Simulink, FreeRTOS, Firebase} \\
                \textbf{Developer Tools}{: Git, Linux, (Neo)Vim, tmux, i3wm, VS Code, Vivado, Jupyter Notebook, Jira, Latex} \\
                \textbf{Libraries}{: Pandas, NumPy, Matplotlib, SciPy, scikit-learn, scikit-image, OpenCV, huggingface, ultralytics} \\
                \textbf{Misc. Skills}{: Altium (PCB design), Solidworks (CAD), ANSYS (FEA), Circuit Analysis, Signal Processing, PID Control, State Space Modelling, Non-linear Control with Lyapunov Functions}, Analysis of MDOF Systems, Modal Analysis, Systems Theoretic Process Analysis (STPA)
          }}
\end{itemize}

%-------------------------------------------
\end{document}
